Network Packet Generation for Artificial Intelligence

### 2020-02-28 paper1/paper1.tex
Added a missing reference

\title{Network packet generation for Artificial Intelligence\\
}

@@

\smallskip To provide better clarity, the individual attack classes, including some examples, are listed again in the following table:

>>>>

\title{Network Packet Generation for Artificial Intelligence}

@@

\smallskip To provide better clarity the individual attack classes, including some examples, are listed in Table \ref{table:attack-types}.:
